Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance

### 2017-03-19 ms_pre_post.Rmd
More minor changes before sending

@@

When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values became substantially higher than in comparable simulations where $F_{a}$ values were fixed to zero and post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H). Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry to the degree that most females mated multiply given low costs of polyandry ($c_{P} < 0.005$; e.g., Figure 2A,B). Hence, given a low cost of polyandry, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D). In contrast, highers cost of polyandry ($c_{P} \geq 0.005$) resulted in initial increases of $P_{a}$ allele values from zero, but then became slightly negative over generations. Trajectories of allele values in individual simulations were typically highly stochastic, but also consistent in long-term direction (Supporting Information pp. S5-S12). Overall, this implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.

>>>>

The empirical examples almost make this worse. It seems like part of our point in the discussion is that indirection selection on polyandry via post-copulatory inbreeding avoidance is possible, but then we already knew that as a result of the empirical examples. Why did we need this model? We need to explain what it is that the model adds in terms of interpretation and theoretical understanding. Just recreating something already observed in empirical studies isn't particularly helpful.

@@

When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values became substantially higher than in comparable simulations where $F_{a}$ values were fixed to zero and post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H). Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry to the degree that most females mated multiply given low costs of polyandry ($c_{P} < 0.005$; e.g., Figure 2A,B). Hence, given a low cost of polyandry, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D). In contrast, higher costs of polyandry ($c_{P} \geq 0.005$) resulted in initial increases of $P_{a}$ allele values from zero, but then became slightly negative over generations. Trajectories of allele values in individual simulations were typically highly stochastic, but also consistent in long-term direction (Supporting Information pp. S5-S12). Overall, this implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.
